% Projects
% Leave this file empty (no content) to hide the section from the CV.

\textbf{ATA Control} \\
\url{https://github.com/Chery-cake/ATA_Control}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Capstone project for IT Technician course: developed a web-based system for managing martial arts tournaments using Java and Spring Boot.
    \item Implemented features for tournament registration, participant management, and automated bracket generation.
    \item Technologies: Spring Boot, Java, MySQL, REST, HTML/CSS, JavaScript.
\end{itemize}

\textbf{Base GDExtension} \\
\url{https://github.com/Chery-cake/base_gdextension}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed a template and build system using CMake for Godot Engine GDExtension modules in C++.
    \item Simplifies setup for Godot extension developers; includes easy integration with external libraries.
    \item Technologies: C++, CMake, Godot Engine.
\end{itemize}

\textbf{Sapphire Gem} \\
\url{https://github.com/Chery-cake/SapphireGem}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Implemented a C++ 3D engine featuring Vulkan-based multi-GPU rendering and modern, multithreaded architecture.
    \item Designed for high performance and scalability in custom graphics applications.
    \item Technologies: C++, Vulkan, VMA, SDL, Slang.
\end{itemize}

\textbf{Freelance Client Backends (2021--2025)} \\
\vspace{-4pt}  
\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed RESTful APIs and backend features using Java (Spring Boot) and SQL for early-stage client prototypes and internal projects.
    \item Technologies: Java, Spring Boot, SQL, Docker, Git.
\end{itemize}

\textbf{Loyalty Poit system for Traveling (2026--2026)} \\
\url{https://github.com/Chery-cake/solochain-template}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed a subtrate to track and manage loyalty points, thru traveling, similar to miles systems
    \item Technologies: Rust, Substrate.
\end{itemize}
